%!TEX root = ../Report.tex

Our project, IChat, is a chatbot coginitive system that will generate related answer for user requests about NUS-ISS programmes, courses and related information.
By using IChat, user can easily get useful and related information from different programmes provided by NUS-ISS.


\section{Improvements} % (fold)
\label{sub:improvements}

With the limited time, our project scope was diminished to a minimum viable product (MVP) level, which is version 1.0. Here is the full scope for the commercial version:

\begin{description}[align=left]
	\item [version 1.1] Include More Data

		To get better result, an advanced method should be used to scrape the data. Add more data fields like lecturers and their detail information for a specific course should be included for a better reply.

	\item [version 1.2] Add API

		An API should be created to fetch dynamic data instead of coding in "Inline Editor" of Dialogflow.

	\item [version 1.3] User Interface

		Although Slack can provide an acceptable user interface, there are still some limit like button length and numbers. Message Menus \cite{messagemenu} could be an option. Even so, for the moment a user needs to use Slack to inquire. Integrating a chatbot like kommunicate \cite{kommunicate}with the NUS-ISS website would help user get a much smoother experience.

	% \item [version 0.5] Fuzzy Logic Improvement

	% 	For miles cards and rewards cards, the current version 0.1 only includes a basic fuzzy logic is used to estimate the cash value of miles and rewards points. To get a better result, detailed data on miles and rewards points conversion are required to match a better cash value.

\end{description}
% section improvements (end)


% \section{Limitations} % (fold)
% \label{sub:limitations}

% As \href{https://www.moneysmart.sg/credit-cards}{MoneySmart} only covers most popular credit cards in Singapore, some credit cards may not be included for the recommendation.

% To simplify the calculation, only long term major features of the cards were included. Some would be manually converted to cash value for comparison.

% As there are some special credit cards for specific groups of people, these cards are excluded in the system. The system also excludes all special term for special employee benefits.

% section limitations (end)